Index measures for oak decline severity using phenotypic descriptors

### 2020-02-09 manuscript/manuscript.Rmd
alteration to site location results section

### Phenotypic differences between site locations

A preliminary analysis using supervised random forest classification could separate trees based on their location (Supplementary  figure 3a; margin = `r site_rf_margin$Margin %>% signif(digits = 3)`). 
The descriptors that contributed most to this discrimination were those that were related to trees size such as DBH, total height and crown radius and likely reflect the varied tree age and planting density across the nine sites (Supplementary figure 3b). 
To counter this, effect sizes were adjusted based on the site means for each tree size descriptor to remove inter-site variability but maintain intra-site variability as described in the Materials and Methods.
After the application of the tree size adjustment, the random forest margin was substantially reduced to `r site_rf_post_correction_margin$Margin %>% signif(digits = 3)` indicating that the adjustment was able to remove the majority of the between site variance.

@@

The complex descriptor interactions within the index models ($M_{PDI}$,$M_{DAI}$) investigated by simulating phenotypic data and generating the index values from the supervised index random forest regression models. 
The index values generated by the models from these simulated phenotypic data were then visualised as model response surface plots, from which descriptor interactions within the indexes can be interpreted. 
Figures 3 and 4 show the simulated index value response surfaces under a variety of different circumstances for key phenotypic descriptors that contribute highly to the PDI and DAI.

>>>>

### Phenotypic differences between site locations and trees size descriptor adjustments

A preliminary analysis using supervised random forest classification could separate trees based on their location (Supplementary  figure 3a) with an average *margin* value of `r site_rf_margin$Margin %>% signif(digits = 3)`.
The descriptors that contributed most to this discrimination were those that were related to trees size such as DBH, total height and crown radius and likely reflect the varied tree age and planting density across the nine sites (Supplementary figure 3b). 
To counter this, effect sizes were adjusted based on the site means for each tree size descriptor to remove inter-site variability but maintain intra-site variability as described in Section #.
This ensures that the subsequent comparisons of these discriptors in the context of oak decline are not confounded by these identified site differences.
After the application of the tree size adjustment, the random forest margin was substantially reduced to `r site_rf_post_correction_margin$Margin %>% signif(digits = 3)` indicating that the adjustment was able to remove the majority of the between site variance.

@@

The complex descriptor interactions within the index models ($M_{PDI}$, $M_{DAI}$) were investigated by simulating phenotypic data and generating the index values from the supervised index random forest regression models. 
The index values generated by the models from these simulated phenotypic data were then visualised as model response surface plots, from which descriptor interactions within the indexes can be interpreted. 
Figures 3 and 4 show the simulated index value response surfaces under a variety of different circumstances for the key phenotypic descriptors described in Section ## that contribute highly to the PDI and DAI.
